Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-11-30 article.qmd
Fix exponent
Change dot to frac derivatives

$$
\dot{x} = -x
$$

@@

$$
\ddot{x} = -x
$$

$$
\begin{cases}
    x(0) &= 1 \\
    \dot{x}(0) &= 0
\end{cases}
$$

Second-order system of an harmonic oscillator,
where the variable `v` stores the derivative $\dot{x}$
and the rate equation is specified for the derivative `v`.
:::

@@

$$
\begin{cases}
    \dot{x} = -x \\
    \dot{y} = -y
\end{cases}
$$

@@

To test the performance,
we simulated them with COPASI, Tellurium/RoadRunner and simbio.
For simbio, we considered both the NumPy and numba backends.
For COPASI and simbio, we used the LSODA solver,
while using the similar CVODE solver for tellurium.
In all cases, we used relative and absolute tolerances of  $10^-6$.
We measured separately three stages of the simulation:
the loading, first/cold run and subsequent/warm runs of each model.

>>>>

$$
\frac{dx}{dt} = -x
$$

@@

$$
\frac{d^2x}{dt^2} = -x
$$

$$
\begin{cases}
    x(0) &= 1 \\
    \frac{dx}{dt}(0) &= 0
\end{cases}
$$

Second-order system of an harmonic oscillator,
where the variable `v` stores the derivative $\frac{dx}{dt}$
and the rate equation is specified for the derivative `v`.
:::

@@

$$
\begin{cases}
    \frac{dx}{dt} = -x \\
    \frac{dy}{dt} = -y
\end{cases}
$$

@@

To test the performance,
we simulated them with COPASI, Tellurium/RoadRunner and simbio.
For simbio, we considered both the NumPy and numba backends.
For COPASI and simbio, we used the LSODA solver,
while using the similar CVODE solver for tellurium.
In all cases, we used relative and absolute tolerances of $10^{-6}$.
We measured separately three stages of the simulation:
the loading, first/cold run and subsequent/warm runs of each model.
